Mainstreaming Race Science

### 2023-07-07 paper/paper.Rmd
paper working notes

*[incorporate def'ns]*
scientific racism 
 ~ purporting to justify racial inequality and colonialism by appealing to the epistemic authority of science

@@

@@

*[this probably goes too far even for a discussion section]*

@@

>>>>

*[incorporate def'ns]*

scientific racism 
 ~ purporting to justify racial inequality and colonialism by appealing to the epistemic authority of science

@@

- pre-20th century history of race concepts and race science
- expansion and contraction of racialized terms over time

@@

*[limitation: colorblind racism (Bonilla-Silva) creates coding ambiguities]*

*[limitation: false negatives (race science papers that don't appear in V24) are possible if, eg, they use many terms related to twin studies of heritability and thereby appear in V03]*

*[replace w/: WinstonWhyMainstreamResearch2020: race science as a community project of psychology(?).  radical academic freedom is a tool used to defend race science PigliucciWhatAreWe2013, RosemanTroublesomeReflectionRacism2014, LarsenMoreProvocativeLess2020.  an important part of how these mainstream journals function as race science echo chambers.]*

@@

*[what can science do? Posselt, /Equity in Science/]*
